## Tibbles

#### data frames vs tibbles

-   Tibbles only show the first 10 rows vertically, and horizontally will display data only as it fits on the screen in columns
-   Tibbles also show their data type for each column (for example: `<chr>` for character, `<dbl>` for doubles)

```{r}
as_tibble(iris)
```

If we need to make a tibble display more columns than it thinks it should, we can override it with print():

```{r}

```

The best way to see more of the data than a tibble default displays is to use View(). Nice!

```{r}

```

#### Subsetting

```{r}

```

At this point, it should be pointed out that the transformation functions from `dplyr` are extremely valuable in context of subsets. In most programming, there are multiple ways of finding the same answer; this applies here as well.

You can also turn a tibble back into a data frame with `as.data.frame()`. This only really comes into play if you're interacting with older code.

## Reading Data

```{r}
view(read_csv("https://github.com/genomicsclass/dagdata/blob/master/inst/extdata/femaleMiceWeights.csv"))
```
